---
title: "Economic Connectedness"
author: "Ali Ahmad"
format: html
echo: false
warning: false
message: false
---
A good looking plot

```{r}

```
A good looking plot





```{r}
#| label: load-packages
#| echo: false
#| message: false
library(primer.data)
library(tidyverse)
```

This plot illustrates the relationship between U.S. county population and economic connectedness, showing that larger populations don't necessarily lead to stronger economic ties. By applying a log scale to the population axis and overlaying a linear regression line, it becomes clear that the trend remains relatively flat—supporting the interpretation that population size has little influence on a county’s economic integration, as suggested by the subtitle.



```{r}
#| label: population-vs-ec
library(scales)
ggplot(data = connectedness, aes(x = population, y = connectedness)) +
  geom_point(color = "black", alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  scale_x_log10(
    breaks = c(1000, 10000, 100000, 1000000, 10000000),
    labels = label_comma()
  ) +
  labs(
    title = "US County Populations versus Economic Connectedness",
    subtitle = "Population size does not matter to EC",
    x = "Population",
    y = "Economic Connectedness",
    caption = "Source: Opportunity Insights"
  ) +
  theme_minimal()


```